---
title: "intro-to-gradr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro-to-gradr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE,message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# What is the `gradr` package about ? 🧑‍🎓🇺🇸👩‍🎓 

The `gradr` package is designed to study and explore the diversity among the PhD graduates in The United States. The purpose of this app is to:

1. study the number of PhD graduates over the time period of study,
2. study the educational diversity of the PhD graduates,
2. study the popular fields of study which yield PhD graduates, and 
3. study the change in gender diversity over the course of the study. 


This vignette will help the user to get started with the package.


## How to install the `gradr` package?

The `gradr` package is available on the github repository and can be installed on your R environment by using the devtools package as follows:

```{r setup, message=FALSE, warning=FALSE}
# Code has been commented out below but can be removed to install the package

# devtools::install_github("devtools::install_github("ETC5523-2023/rpkg-arinbaruah"))
```

Once the library has been successfully installed in your R environment, you can load the R package as follows:

```{r}
library(gradr)
```

The `gradr` package has tons of exciting stuff you can explore ! 🤩🥳 

Some of the key features are explained here:

### Access the data for the PhD field of study in US

The `gradr` package includes a dataset `us_phd_field`, a dataframe with **3370 rows** and **5 variables**. The data can be obtained through the code chunk below:

```{r eval=FALSE}
gradr::us_phd_field
```

Let us provide you with a glimpse of the dataset:

```{r field, message=FALSE, warning=FALSE}
library(dplyr)
glimpse(us_phd_field)
```
You can refer to the documentation of the dataset through the codechunk below:

```{r eval=FALSE}
help("us_phd_field")
```


Hold on ! We have another exciting dataset for you to explore. 

### Access the data for the gender of PhD graduates in the US

The `gradr` package includes a dataset `us_phd_gender`, a dataframe with **53 rows** and **4 variables**. The data can be obtained through the code chunk below:

```{r eval=FALSE}
gradr::us_phd_gender
```

Let us provide you with a glimpse of the dataset:

```{r gender, message=FALSE, warning=FALSE}
library(dplyr)
glimpse(us_phd_gender)
```

More details about this dataset can be found by using the code `help("us_phd_gender")`.

### Run the US PhD graduate R Shiny Application

To run the R shiny application, with the following code:

```{r gradapp, eval = FALSE}
grad_app()
```

More information about how to use the app can be found in the **about** section of the application. You can refer to the brief help section by running the code `help("grad_app")`.

### Caclulate the number of graduates in a field of study

The package contains a function `calc_grads` to calculate the number of PhD graduates in a specific field of study without having to use the R shiny application. The argument of the function accepts a field of study currently undertaken in the US as per the data. The function can be used as follows: 

- `calc_grads()` : calculates the total number of PhD graduates for the input field of study present in the database. 

```{r calcgrad}
calc_grads("Agricultural economics")
```
For more details : `help(calc_grads)`

## Further Information

For detailed information of the `gradr` package, please visit the [pkgdown](https://etc5523-2022.github.io/rpkg-jval0011/) site.

